---
title: "Nudging participation in the Payments for Environmental Services Program in the EU"
output: html_document
---

```{r libs, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE,results=FALSE}
library(tidyverse)
library(RMySQL)
```

[Chabe-Ferret et al (2022)](file:///Users/sylvain/Dropbox/private/Private/projets_papiers/Environnement/PENSEE/COLLABORATIONS/Hauts_de_France/WORK/HdF_ReAnalysis_Publication.html) report on the results of a large randomised experiment (N=20000) conducted in the Hauts de France region to test whether nudges sent by mail can increase the subscription rate of Payments for Environmental Services 
they test several nudges: 

  - Treatment 1: information about the program.
  - Treatment 2: testimonies by farmers already benefiting from the program.
  - Treatment 3: pre-stamped reply forms.

```{r MainChabe, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE,results=FALSE}
# reading connection informations
source(here::here("idSQL.R"))
# connecting to SQL server
HdF <- dbConnect(MySQL(), dbname="HdF",
                     user=myid, password=mypass, host=myhost)
# reading Results table
chabe <- dbReadTable(HdF,"Results") %>%
              mutate(
                   Treatment=factor(Treatment,levels=c("All","Bare Letter","Bare Letter+Testimonies","Bare Letter+Testimonies+Pre-Stamped Reply Form","Testimonies vs Bare Letter","Testimonies+Pre-Stamped Reply Form vs Bare Letter","Pre-Stamped Reply Form vs Testimonies")),
                  Treatment= factor(as.character(as.numeric(Treatment)-1),levels=as.character(0:6)),
                  Treatment=recode(Treatment,"0"="All"
                                            ,"4"="2vs1"
                                            ,"5"="3vs1"
                                            ,"6"="3vs2")
                  )

# disconnecting the connection to the SQL server
dbDisconnect(HdF)
```

```{r MainChabePlot, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE,results=FALSE,fig.cap=c('Impact and cost-effectiveness of the treatments'),fig.subcap=c('Treatment effects','Cost-effectiveness'),fig.align='center', out.width="50%", fig.height=4, fig.width=6}
# generating plot for treatment effects
ggplot(filter(chabe,Outcome=="Contracts"),aes(Treatment,TE)) +
  geom_pointrange(aes(ymin=TE-1.96*SeTE,ymax=TE+1.96*SeTE),position=position_dodge(0.7))+
 ylab("Number of additional contracts (per 10000 letters)")+
  theme_bw()

# generating plot for cost-effectiveness
ggplot(filter(chabe,Treatment=="All"|Treatment=="1"|Treatment=="2"|Treatment=="3"),aes(Treatment,CE)) +
  geom_pointrange(aes(ymin=CE-1.96*SeCE,ymax=CE+1.96*SeCE),position=position_dodge(0.7))+
  coord_cartesian(ylim=c(0,600))+
 ylab("Cost per additional contract (in 2018 Euros)")+
  xlab("Treatment")+
  theme_bw()

```

Chabe-Ferret et al (2022) find that:

  1. Simple letters informing farmers that they are eligible to PES increase the number of contracts by `r chabe %>% filter(Outcome=='Contracts',Treatment=='1') %>% pull(TE) %>% round(.,0)` $\pm$ `r 2*(chabe %>% filter(Outcome=='Contracts',Treatment=='1') %>% pull(SeTE) %>% round(.,0))` per 10000 letters sent, at a cost of  `r chabe %>% filter(Outcome=='Contracts',Treatment=='1') %>% pull(CE) %>% round(.,0)` $\pm$ `r 2*(chabe %>% filter(Outcome=='Contracts',Treatment=='1') %>% pull(SeCE) %>% round(.,0))` *2018 Euros*/additional contract, without degrading the environmental quality of the contracts.
  2. Nudges such as testimony or social comparison does not result in additional contracts on top of the simple letter (`r chabe %>% filter(Outcome=='Contracts',Treatment=='2vs1') %>% pull(TE) %>% round(.,0)` $\pm$ `r 2*(chabe %>% filter(Outcome=='Contracts',Treatment=='2vs1') %>% pull(SeTE) %>% round(.,0))` per 10000 letters).
  3. Pre-stamped reply forms increase contacts with caseworkers on top of the simple letter (`r chabe %>% filter(Outcome=='Contacts',Treatment=='3vs1') %>% pull(TE) %>% round(.,0)` $\pm$ `r 2*(chabe %>% filter(Outcome=='Contacts',Treatment=='3vs1') %>% pull(SeTE) %>% round(.,0))` per 10000 letters) but do not increase the number of contracts (`r chabe %>% filter(Outcome=='Contracts',Treatment=='3vs1') %>% pull(TE) %>% round(.,0)` $\pm$ `r 2*(chabe %>% filter(Outcome=='Contracts',Treatment=='3vs1') %>% pull(SeTE) %>% round(.,0))` per 10000 letters).
